Considering scale in multilayer animal social networks

### 2020-08-25 paper/manuscript.Rmd
add evans 2019 to social scale p

Social interactions exists across both temporal and spatial scales [Figure \@ref(fig:spacetime), @Whitehead_2008].
For example, conspecific grooming requires close spatial proximity and occurs over brief time periods [e.g. @Carter_2015] whereas <!--Social
associations occur over longer time periods and represent
whereas social associations over longer time periods represent shared space use by
members of the same social group [Figure \@ref(fig:spacetime), @Franks_2009].
<!--Individuals must share space to interact or associate and thus have overlapping
home ranges [@Vander_2014].--> home range overlap and shared space use occur over
coarser spatial and temporal scales [e.g. @Piza_Roca_2018].
Although the social environment scales spatially and temporally, it
remains unclear whether coarser scales of social interactions, such as social
association and home range overlap, vary predictably [@Castles_2014;
@Farine_2015a]. Social scale 
is defined by the temporal and spatial scales across which different forms of sociality are measured  [@Farine_2015a].

>>>>

Social interactions exists across both temporal and spatial scales [Figure \@ref(fig:spacetime), @Whitehead_2008].
For example, conspecific grooming requires close spatial proximity and occurs over brief time periods [e.g. @Carter_2015] whereas social associations
represent shared space use by members of the same social group over longer time periods [@Franks_2009], and home range overlap occurs over
coarser spatial and temporal scales [e.g. @Piza_Roca_2018].
Although the social environment scales spatially and temporally, it
remains unclear whether coarser scales of social interactions, such as social
association and home range overlap, vary predictably [@Castles_2014;
@Farine_2015a; @Evans_2019]. Social scale 
is defined by the temporal and spatial scales across which different forms of sociality are measured  [@Farine_2015a].
